Mining Planet Search Data for Binary Stars: The $\psi^1$ Draconis system

### 2015-10-22 paper/ms.tex
Removed Figures 4+5 (the posteriors)

\title{Mining Planet Search Data for Binary Stars: The $\psi^1$ Draconis system [UPDATE PLOTS!]}
\author{Kevin Gullikson \altaffilmark{1}}
%\affil{University of Texas, Department of Astronomy \email{kgulliks@astro.as.utexas.edu}}
\author{Michael Endl \altaffilmark{1}}
\author{William D. Cochran \altaffilmark{1}}
\author{Phillip J. MacQueen \altaffilmark{1}}

\altaffiltext{1}{University of Texas}

@@

The model temperature was chosen based on high contrast imaging in Brugameyer et al (2015), which finds a companion with approximately that temperature. We shift each CCF so that the dominant peak, which signifies the match of the M-star model template with the F-type primary star, falls at $v=0$. This effectively puts the cross-correlation functions in the rest frame of the primary star, although there is a constant velocity offset because the observed spectra are wavelength-calibrated to air wavelengths, while the model spectra is calculated in vacuum wavelengths. We shift the model spectra to air wavelengths using an approximate formula \citep{Ciddor96}, but expect a small difference between the calculated and actual index of refraction since the observatory is at a higher altitude with correspondingly lower air pressure than where the conversion formula was calibrated. The difference in index of refraction translates into a velocity offset, which we denote as $\Delta v_2$ in later sections of this paper.

@@

The companion radial velocities are measured relative to the primary star plus a small velocity shift ($\Delta v_2$) caused by a slight inaccuracies in the vacuum to air wavelength conversion in the model spectrum. Finally, the CCF peak full-width at half maximum vastly over-estimates the velocity uncertainty and so we fit a scale factor ($f$) to apply to the companion velocity uncertainties. The uncertainties given in Table \ref{tab:rv_data} are already scaled by this factor. The full log-likelihood function ($\mathcal{L}$) is then given by:

@@

We use the affine invariant sampler provided in the emcee code \citep{emcee} to perform a Markov Chain Monte Carlo (MCMC) fit to all of the parameters described above. We use flat priors in all variables except for the RV jitter and companion rv uncertainty scale factors ($\sigma_J$ and $f$, respectively), for which we use log-uniform priors to allow for a large range of values.  We give the median value and uncertainty for each parameter in Table \ref{tab:orbit}. The uncertainties are estimated from the posterior probability distribution samples such that the lower and upper bounds give the 16th and 84th percentile (i.e. they are $1\sigma$ credibility intervals). We plot the best-fit orbit with the data in Figure \ref{fig:orbit}, with the uncertainties on the companion velocities scaled and the velocities shifted by $\Delta v_1$ and $\Delta v_2$. We show the posterior probability distributions for the orbital parameters in Figure \ref{fig:orbit_dist} and for the data shifting and scaling parameters ($\Delta v_1$, $\Delta v_2$, and the uncertainty scaling) in Figure \ref{fig:datamanip_dist}.

@@

We use the radial velocity measurements for both the primary and secondary stars to find an orbital solution to the now double-lined spectroscopic binary. The summary values and posterior probability distributions of the fitted parameters are given in Table \ref{tab:orbit} and Figures \ref{fig:orbit_dist} and \ref{fig:datamanip_dist}. Finally, we report the mass and expected temperature of the companion as well as the orbital inclination and semi-major axis. The temperature agrees well with high contrast imaging, validating our method.

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{Distributions_1.pdf}
  \caption{MCMC samples from the posterior distributions for the orbital parameters.}
  \label{fig:orbit_dist}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{Distributions_2.pdf}
  \caption{MCMC samples from the posterior distributions for the data shift and scaling parameters.}
  \label{fig:datamanip_dist}
\end{figure}

>>>>

\title{Mining Planet Search Data for Binary Stars: The $\psi^1$ Draconis system}
\author{Kevin Gullikson \altaffilmark{1}}
%\affil{University of Texas, Department of Astronomy \email{kgulliks@astro.as.utexas.edu}}
\author{Michael Endl \altaffilmark{1}}
\author{William D. Cochran \altaffilmark{1}}
\author{Phillip J. MacQueen \altaffilmark{1}}

\altaffiltext{1}{University of Texas, Astronomy Department. 2515 Speedway, Stop C1400. Austin, TX 78712 \email{kgulliks@astro.as.utexas.edu}}

@@

The model temperature was chosen based on high contrast imaging in Brugameyer et al (2015), which finds a companion with approximately that temperature. We shift each CCF so that the dominant peak, which signifies the match of the M-star model template with the F-type primary star, falls at $v=0$. This effectively puts the cross-correlation functions in the rest frame of the primary star, although there is a constant velocity offset caused by small errors in the vacuum to air wavelength conversion and spectrograph wavelength drift throughout the night. We denote this shift as $\Delta v_2$ in later sections of this paper.

@@

The companion radial velocities are measured relative to the primary star plus a small velocity shift ($\Delta v_2$) caused by a slight inaccuracies in the vacuum to air wavelength conversion in the model spectrum and spectrograph wavelength drift throughout the night. Finally, the CCF peak full-width at half maximum vastly over-estimates the velocity uncertainty and so we fit a scale factor ($f$) to apply to the companion velocity uncertainties. The uncertainties given in Table \ref{tab:rv_data} are already scaled by this factor. The full log-likelihood function ($\mathcal{L}$) is then given by:

@@

We use the affine invariant sampler provided in the emcee code \citep{emcee} to perform a Markov Chain Monte Carlo (MCMC) fit to all of the parameters described above. We use flat priors in all variables except for the RV jitter and companion rv uncertainty scale factors ($\sigma_J$ and $f$, respectively), for which we use log-uniform priors to allow for a large range of values.  We give the median value and uncertainty for each parameter in Table \ref{tab:orbit}. The uncertainties are estimated from the posterior probability distribution samples such that the lower and upper bounds give the 16th and 84th percentile (i.e. they are $1\sigma$ credibility intervals). We plot the best-fit orbit with the data in Figure \ref{fig:orbit}, with the uncertainties on the companion velocities scaled and the velocities shifted by $\Delta v_1$ and $\Delta v_2$.

@@

We use the radial velocity measurements for both the primary and secondary stars to find an orbital solution to the now double-lined spectroscopic binary. The summary values of the fitted parameters are given in Table \ref{tab:orbit}. Finally, we report the mass and expected temperature of the companion as well as the orbital inclination and semi-major axis. The temperature agrees well with high contrast imaging, validating our method.

@@
